Supporting Information for "Imperfect slope measurements drive overestimation in geometric cone model of lake and reservoir depth"

### 2021-12-07 manuscript/si_template_2019.tex
formatting toc for consistency

            \item \textbf{Figure S2:} Effect of calculation technique on in-lake/nearshore slope comparison.

@@

            \item \textbf{Figure S7:} Spatial distribution of depth model residuals.

@@

            \item \textbf{Table S1:} Effect of calculation technique on depth model fit and accuracy.

>>>>

            \item \textbf{Figure S2:} Effect of calculation technique on in-lake/nearshore slope comparison

@@

            \item \textbf{Figure S7:} Spatial distribution of depth model residuals

@@

            \item \textbf{Table S1:} Effect of calculation technique on depth model fit and accuracy
